%!TEX program = xelatex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\newenvironment{citemize}{\begin{itemize}[leftmargin=12pt]\vspace{-10pt}}{\end{itemize}}
\usepackage{enumitem}

\begin{document}

\header{Jiahao }{Li}{} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
room 3-2-702 shuahu residential quarter
no. 315 xudong st.
wuhan, hubei, china
~
+1 (702) 237-0094
+86 18607160420
~
\href{mailto:isundaylee@gmail.com}{isundaylee@gmail.com}
\href{http://ljh.me}{http://ljh.me}
~
\section{languages}
native in mandarin
fluent in english
~
\section{computer skills}
c/c++(major), objective-c, ruby, php, html/css, python, visual basic, pascal
~
\section{interests}
music composition
~
national level 9 (highest) certificate of jazz drum
~
national level 8 certificate of piano
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{2013-Present}
{Tufts University Preparatory Program, Medford, MA}
{}
{\begin{citemize}
  \item{Courses: Academic Writing, Academic Reading, Academic Speaking, COMP 163 Computational Geometry (Auditing)}
\end{citemize}}
%------------------------------------------------
\entry
{2011-Present}
{Wuhan Foreign Languages School, Wuhan, China}
{High School}
{\begin{citemize}
  \item{AP Courses: Computer Science A (5), Calculus BC (5), Physics C Mechanics (5), Physics C Electricity \& Magnetism (5), Microeconomics (5), Macroeconomics(5), Statistics (5)}
  \item{Percentile: Top 1\%}
  \item{Standardized Tests: \\
    TOEFL: 116 (Reading: 30 Listening: 30 Writing: 29 Speaking: 27)\\
    SAT I: 2340 (Reading: 740 Maths: 800 Writing: 800) \\
    SAT II: 2400 (Math Level II: 800 Physics: 800 Chemistry: 800)}
\end{citemize}}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{research}

\begin{entrylist}
%------------------------------------------------
\entry
{Summer 2013}
{``Interference Minimization Problem of Computational Geometry''}
{Tufts University}
{\begin{citemize}
  \item{Mentored by Prof. Csaba Toth}
  \item{Identified similarities between interference minimization and processor task scheduling. }
  \item{Designed and simulated a dynamic programming algorithm for interference minimization. }
\end{citemize}}
%------------------------------------------------
\entry
{Summer 2012}
{``Cellular Automata''}
{Tufts University}
{\begin{citemize}
  \item{Mentored by Prof. Diane Souvaine \& Ph. D. Andrew Winslow}
\end{citemize}}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{projects}

\begin{entrylist}
%------------------------------------------------
\entry
{2013}
{WFLSSU, Designer and Coder}
{}
{A site for my school's Students' Union to manage its membership profiles and to streamline its workflow. Coded with Ruby on Rails. (\href{http://github.com/isundaylee/wflssu}{Link to Code})}
%------------------------------------------------
\entry
{2012}
{VOCABI iOS App, Designer and Coder}
{}
{An iPhone/iPad app for English learners to enlarge vocabulary. (\href{http://github.com/isundaylee/vocabi-ios}{Link to Code})}
%------------------------------------------------
\entry
{2012}
{WFLSer Alumni Site, Co-Founder, Designer \& Coder}
{}
{Designed and maintained an alumni socializing site for my high school. \\
Designed development and publicity plans for the site. (\href{http://github.com/isundaylee/alumni}{Link to Code})}
%------------------------------------------------
\entry
{2011}
{VIROJ, Designer and Coder}
{}
{An online code evaluating system for judging ACM/ICPC style problems. }
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{honors \& awards}

%------------------------------------------------
\subsection{}{General}
\begin{entrylist}
%------------------------------------------------
\centry
{Sept. 2011}
{4th Annual Wenhua Technology Award (top 10 among all high school students in Hubei province)}
%------------------------------------------------
\centry
{Aug. 2011}
{Early acceptance into Peking University School of Electronic Engineering and Computer Science}
%------------------------------------------------
\centry
{Feb. 2011}
{Early acceptance into Xi'an Jiaotong University through talented-youth-early-admission program. Ranked 1st among 1260 applicants. }
%------------------------------------------------
\end{entrylist}
\subsection{}{Olympiad in Informatics}
\begin{entrylist}
%------------------------------------------------
\centry
{Nov. 2011}
{17th National Olympiad in Informatics, 1st Place in Hubei Province}
%------------------------------------------------
\centry
{Aug. 2011}
{28th National Olympiad in Informatics, First Prize \\
Selected into IOI China National Team Training Camp \\
First Hubei province contestant to win it in 6 years. }
%------------------------------------------------
\centry
{May 2011}
{Asia-Pacific Informatics Olympiad (China Region), Bronze Medal}
%------------------------------------------------
\centry
{Nov. 2010}
{16th National Olympiad in Informatics, Provincial First Prize}
%------------------------------------------------
\end{entrylist}
\subsection{}{Olympiad in Mathematics}
\begin{entrylist}
%------------------------------------------------
\centry
{Apr. 2013}
{American Invitational Mathematics Examination (AIME), score 12/15. USAMO qualifier. Worldwide percentile 97\%. }
%------------------------------------------------
\centry
{Feb. 2013}
{American Mathematics Competition (AMC) 12 Distinguished Honor (Worldwide Top 1\%). }
%------------------------------------------------
\centry
{Nov. 2012}
{High School Mathematical Contest in Modeling (HiMCM), Meritorious Award}
%------------------------------------------------
\centry
{Apr. 2010}
{National Middle School Mathematics League, Second Prize}
%------------------------------------------------
\end{entrylist}
\subsection{}{Olympiad in Physics}
\begin{entrylist}
%------------------------------------------------
\centry
{Apr. 2011}
{National Physics Contest, First Prize}
%------------------------------------------------
\end{entrylist}


%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{extracurriculars}

\begin{entrylist}
%------------------------------------------------
\entry
{2013}
{AP Computer Science, Volunteering Instructor}
{}
{\begin{citemize}
  \item{Taught official school AP Computer Science course. }
  \item{Including Java fundamentals, object-oriented concept and algorithms. }
  \item{Helped 2 students win Second Prize in National Olympiad in Informatics. }
\end{citemize}}
%------------------------------------------------
\entry
{2012-2013}
{Student Council, Presidential Committee Member \& Technical Counselor}
{}
{\begin{citemize}
    \item{Designed WFLSSU for membership management. }
    \item{Designed and implemented workflow electronization plans. }
  \end{citemize}}
%------------------------------------------------
\entry
{2009-2011}
{Beetle IT Enthusiasts Club, Co-founder}
{}
{\begin{citemize}
    \item{Developed computer-aided teaching software for teachers. }
    \item{Provided computer programming courses for students. }
    \item{Awarded the Most Creative Club at school. }
    \item{I myself awarded Most Influential Club Leader. }
  \end{citemize}}

%------------------------------------------------
\entry
{2004-2010}
{School Orchestra, Drummer and Marimba Player}
{}
{\begin{citemize}
  \item{Participated in regular practices. }
  \item{Performed on major celebrations and festivals on campus. }
\end{citemize}}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{publication}

[1] Jiahao Li, ``From Floyd to SPFA'', National Olympiad in Informatics (NOI) Journal, p. 22-23, Dec. 2011. (In Chinese)

%----------------------------------------------------------------------------------------

\end{document}